---
title: "vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message = FALSE}
library(FinalProject)
library(tidyverse)
library(devtools)
load_all()
```

This package is contributed by Zhuoheng Han, Christopher Ton, Samuel Krut and Valerie Tu.

Our package enables other users to carry out bag-of-little-boostraps for the multiple linear regression model. This package gives users the ability use parallel processing to obtain the  confidence interval of sigma, coefficients, and prediction intervals. Users can decide group numbers and the times of bootstraps in this package.

In the instance that users have problems on how to use our functions, please use `?coef_ci`, `?sigma_ci`, and `?pred_ci` to learn more about the usage and variables. We have also included an example for each function.

```{r, message = FALSE}
?coef_ci
?sigma_ci
?pred_ci
```

Here we use part of the flights data in library(nycflights13) to illustrate how to use our package. Here is what our data and newdata look like. We choose `dep_delay`, `arr_delay`, and `distance` as independent variables and we combine `hour` and `minute` into `time` as the response variable. 

```{r, message = FALSE}
library(nycflights13)
flights = flights %>%
  mutate(time = hour*60 + minute) %>%
  select(dep_delay,arr_delay,distance,time)
y = flights$time #response variable defined
x = flights[,c(1:3)] #predictor variables subsetted
data = data.frame(y,x)
newdata = data.frame(dep_delay = c(10,20), arr_delay = c(20,30), distance = c(400,500))
```

First, we apply the `coef_ci` function to find the confidence interval of each coefficient. Users can decide group numbers and times of bootstraps. In this instance we will use group_number = 10 and boostraps_times = 100 as an example. (Also, for the `pred_ci` and `sigma_ci`)

```{r, message = FALSE, warning = FALSE}
coef_ci(data, 10, 100)
summary(lm(y~., data))$coef[,1]
```

Then, let us check how `pred_ci` function works.
```{r, message = FALSE, warning = FALSE}
pred_ci(data, newdata, 10, 100)
predict(lm(y~., data), newdata)
```
